NMRlipids Databank makes data-driven analysis of biomembrane properties accessible for all

### 2023-03-28 main.tex
Update text

\subsection{Analysing simulations}
In practise, simulations in the NMRlipids databank can be analyzed by executing a program that loops over README.yaml files in the {\it databank layer}, downloads the data using the information in README.yaml files, and then performs the desired analysis on a local computer utilising the universal naming conventions for molecules and atoms defined in README.yaml and mapping files. This procedure is illustrated in Fig.~\ref{fig:overlay}D and examples of codes that perform such analyses in practise are listed in tables~\ref{tab:codes} and~\ref{tab:codesApplication}.

@@

To streamline the comparison between simulations, we define the qualities for different fragments (frag = \textit{sn}-1, \textit{sn}-2, headgroup or total referring to all order parameters within a molecule) within each lipid type in a simulation as
\begin{equation}
    P^\mathrm{frag}[\mathrm{lipid}] = \langle P[\mathrm{lipid}]\rangle_\mathrm{frag} F_\mathrm{frag}[\mathrm{lipid}],
\end{equation}
where $\langle P[\mathrm{lipid}]\rangle_\mathrm{frag}$ is the average of individual C-H bond order parameters qualities within the fragment, and $F_\mathrm{frag}[\mathrm{lipid}]$ is the percentage of order parameters for which the quality is available within the fragment.
%, and frag can be \textit{sn}-1, \textit{sn}-2, headgroup or total (all order parameters within a molecule). 
The overall quality of different fragments in a simulation are then defined as a molar fraction weighted average over different lipid components
\begin{equation}
    P^\mathrm{frag} = \sum_\mathrm{lipid} \chi_\mathrm{lipid} P^\mathrm{frag}[\mathrm{lipid}],
\end{equation}
where $\chi_\mathrm{lipid}$ is the molar fraction of a lipid in the bilayer.

>>>>

\subsection{Analysing simulations}
In practise, simulations in the NMRlipids databank can be analyzed by executing a program that loops over README.yaml files in the {\it databank layer}, downloads the data using the information in README.yaml files, and then performs the desired analysis on a local computer utilising the universal naming conventions for molecules and atoms defined in README.yaml and mapping files. This procedure is illustrated in Fig.~\ref{fig:overlay}D and examples of codes that perform such analyses in practise are listed in tables~\ref{tab:codes} and~\ref{tab:codesApplication}. The equilibration period given by the user (TIMELEFTOUT in table~\ref{tab:READMEkeys}) is discarded from the trajectories in all analysis codes.

@@

To streamline the comparison between simulations, we define the qualities for different fragments (frag = \textit{sn}-1, \textit{sn}-2, headgroup or total referring to all order parameters within a molecule) within each lipid type in a simulation as
\begin{equation}
    P^\mathrm{frag}[\mathrm{lipid}] = \langle P[\mathrm{lipid}]\rangle_\mathrm{frag} F_\mathrm{frag}[\mathrm{lipid}],
\end{equation}
where $\langle P[\mathrm{lipid}]\rangle_\mathrm{frag}$ is the average of individual C-H bond order parameters qualities within the fragment, and $F_\mathrm{frag}[\mathrm{lipid}]$ is the percentage of order parameters for which the quality is available within the fragment.
%, and frag can be \textit{sn}-1, \textit{sn}-2, headgroup or total (all order parameters within a molecule). 
The overall quality of different fragments in a simulation (frag = tails, headgroup or total) are then defined as a molar fraction weighted average over different lipid components
\begin{equation}
    P^\mathrm{frag} = \sum_\mathrm{lipid} \chi_\mathrm{lipid} P^\mathrm{frag}[\mathrm{lipid}],
\end{equation}
where $\chi_\mathrm{lipid}$ is the molar fraction of a lipid in the bilayer and "tails" refer to the average of all acyl chains.
